Active Learning for Level Set Estimation

### 2013-03-22 msthpres.tex
Reduce/simplify theory

\subsection*{Theoretical analysis}
\begin{frame}
How do we judge the ``accuracy'' of a solution $(\hat{H}, \hat{L})$?
\uncover<2->{
\begin{definition}[Misclassification loss]
%\begin{align*}
$\ell_h(\*x) = \twopartdef{\max\{0, f(\*x) - h\}}{\*x\in \hat{L}}{\max\{0, h - f(\*x)\}}{\*x\in \hat{H}}$
%\end{align*}
\end{definition}
\begin{center}
\includegraphics[width=3.5in]{figures/misclass}
\end{center}
}
\end{frame}

\begin{frame}
\footnotesize
\begin{tikzpicture}[node distance=1cm, auto,]
 \uncover<1->{
 \node[st] (conv) {Convergence};
 }

 \uncover<3->{
 \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
   edge[pil] (conv);
 }

 \uncover<4->{
 \node[st,text width=14em,below=3em of clas] (amb)
 {\makecell[c]
   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
    get small enough ($<2\epsilon$)\uncover<12->{:\\[0.5em]
    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
    }
   }
 } edge[pil] (clas);

 \uncover<4->{ 
 \node[st,right=1.5em of clas] (eps) {$\epsilon$}
   edge[pil] (amb);
 }

 \uncover<18->{ 
 \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
   edge[pil] (amb);
 }

 \node[st,draw=none,below=3em of amb] (dummy) {};
 }

 \uncover<11->{
 \node[st,left=1.5em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 }

 \uncover<5->{
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 }

 \uncover<6->{
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 }

 \uncover<7->{
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 }

 \uncover<8->{
 \node[st,right=3em of t3] (t4) {$\beta_t$}
   edge[pil] (amb);
 }

 \uncover<18->{
 \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
   edge[pil] (amb);
 }

 \uncover<9->{
 \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}

 \uncover<9->{
 \node[st,below=3em of fit1] (gamma)
 {\makecell[c]
   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<10->{\\[0.5em]
    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
    }
   }
 } edge[pil] (fit1);
 }

 \uncover<2->{
 \node[st,right=9em of conv] (acc) {Solution accuracy};
 }

 \uncover<14->{
 \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
   edge[pil] (acc)
   edge[pil,<-] (eps);
 }

 \uncover<15->{
 \node[st,right=1.5em of loss] (rules) {Class. rules}
   edge[pil] (loss);
 }

 \uncover<16->{ 
 \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
   edge[pil] (loss);
 }

 \uncover<16->{ 
 \node[st,right=1.5em of est] (delta) {$\delta$}
   edge[pil] (est);
 }

 \uncover<17->{
 \node[st,below=3em of est] (large) {Conf. intervals are large enough}
   edge[pil] (est)
   edge[pil,<-] (t4);
 }
\end{tikzpicture}
\end{frame}

\begin{frame}
\begin{theorem}[Convergence of \acl]
\label{thm:acl}
For any $h\in\mathbb{R}$, $\delta \in (0, 1)$, and $\epsilon > 0$,
if $\beta_t = 2\log(|D|\pi^2 t^2/(6\delta))$, \acl terminates after
at most $T$ iterations, where $T$ is the smallest positive integer
satisfying
\begin{align*}
\frac{T}{\beta_T \gamma_T} \geq \frac{C_1}{4\epsilon^2},
%T/(\beta_T \gamma_T) \geq C_1/(4\epsilon^2),
\end{align*}
where $C_1 = 8 / \log(1 + \sigma^{-2})$.

@@

>>>>

\subsection*{Theoretical analysis}
%\begin{frame}
%How do we judge the ``accuracy'' of a solution $(\hat{H}, \hat{L})$?
%\uncover<2->{
%\begin{definition}[Misclassification loss]
%%\begin{align*}
%$\ell_h(\*x) = \twopartdef{\max\{0, f(\*x) - h\}}{\*x\in \hat{L}}{\max\{0, h - f(\*x)\}}{\*x\in \hat{H}}$
%%\end{align*}
%\end{definition}
%\begin{center}
%\includegraphics[width=3.5in]{figures/misclass}
%\end{center}
%}
%\end{frame}

%\begin{frame}
%\footnotesize
%\begin{tikzpicture}[node distance=1cm, auto,]
% \uncover<1->{
% \node[st] (conv) {Convergence};
% }
%
% \uncover<3->{
% \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
%   edge[pil] (conv);
% }
%
% \uncover<4->{
% \node[st,text width=14em,below=3em of clas] (amb)
% {\makecell[c]
%   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
%    get small enough ($<2\epsilon$)\uncover<12->{:\\[0.5em]
%    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
%    }
%   }
% } edge[pil] (clas);
% 
% \uncover<4->{ 
% \node[st,right=1.5em of clas] (eps) {$\epsilon$}
%   edge[pil] (amb);
% }
% 
% \uncover<18->{ 
% \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
%   edge[pil] (amb);
% }
% 
% \node[st,draw=none,below=3em of amb] (dummy) {};
% }
%
% \uncover<11->{
% \node[st,left=1.5em of amb] (t0) {Monotonicity}
%   edge[pil] (amb);
% }
% 
% \uncover<5->{
% \node[st,left=3em of dummy] (t1) {Samples ($t$)}
%   edge[pil] (amb);
% }
% 
% \uncover<6->{
% \node[st,right=1em of t1] (t2) {Kernel ($k$)}
%   edge[pil] (amb);
% }
% 
% \uncover<7->{
% \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
%   edge[pil] (amb);
% }
% 
% \uncover<8->{
% \node[st,right=3em of t3] (t4) {$\beta_t$}
%   edge[pil] (amb);
% }
% 
% \uncover<18->{
% \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
%   edge[pil] (amb);
% }
% 
% \uncover<9->{
% \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
% 
% \uncover<9->{
% \node[st,below=3em of fit1] (gamma)
% {\makecell[c]
%   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
%    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<10->{\\[0.5em]
%    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
%    }
%   }
% } edge[pil] (fit1);
% }
%
% \uncover<2->{
% \node[st,right=9em of conv] (acc) {Solution accuracy};
% }
%
% \uncover<14->{
% \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
%   edge[pil] (acc)
%   edge[pil,<-] (eps);
% }
%
% \uncover<15->{
% \node[st,right=1.5em of loss] (rules) {Class. rules}
%   edge[pil] (loss);
% }
%
% \uncover<16->{ 
% \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
%   edge[pil] (loss);
% }
%
% \uncover<16->{ 
% \node[st,right=1.5em of est] (delta) {$\delta$}
%   edge[pil] (est);
% }
%
% \uncover<17->{
% \node[st,below=3em of est] (large) {Conf. intervals are large enough}
%   edge[pil] (est)
%   edge[pil,<-] (t4);
% }
%\end{tikzpicture}
%\end{frame}

%\begin{frame}
%\footnotesize
%\begin{tikzpicture}[node distance=1cm, auto,]
% \uncover<1->{
% \node[st] (conv) {Convergence};
% }
%
% \uncover<1->{
% \node[st,below=3em of conv] (clas) {All points in $D$ have been classified}
%   edge[pil] (conv);
% }
%
% \uncover<1->{
% \node[st,text width=14em,below=3em of clas] (amb)
% {\makecell[c]
%   {Conf. intervals ($\Leftrightarrow$ ambiguities)\\
%    get small enough ($<2\epsilon$)\uncover<1->{:\\[0.5em]
%    $a_t(\*x_t) \sim \mathcal{O}\left(\sqrt{\displaystyle\frac{\beta_t\gamma_t}{t}}\right)$
%    }
%   }
% } edge[pil] (clas);
% 
% \uncover<1->{ 
% \node[st,right=1.5em of clas] (eps) {$\epsilon$}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{ 
% \node[st,right=1.5em of clas,fill=c6] (eps) {$\epsilon$}
%   edge[pil] (amb);
% }
% 
% \node[st,draw=none,below=3em of amb] (dummy) {};
% }
%
% \uncover<1->{
% \node[st,left=1.5em of amb] (t0) {Monotonicity}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[st,left=3em of dummy] (t1) {Samples ($t$)}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[st,right=1em of t1] (t2) {Kernel ($k$)}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[st,right=3em of t3] (t4) {$\beta_t$}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[st,right=3em of t3,fill=c6] (t4) {$\beta_t$}
%   edge[pil] (amb);
% }
% 
% \uncover<1->{
% \node[draw=black,densely dotted,line width=0.7pt,fit=(t1)(t3)] (fit1) {};}
% 
% \uncover<1->{
% \node[st,below=3em of fit1] (gamma)
% {\makecell[c]
%   {Quantify by max. information gain (Srinivas \emph{et al.}, 2010):\\[0.5em]
%    $\gamma_t = \max_{\*y_t} I(\*y_{1:t}; f)$\uncover<1->{\\[0.5em]
%    For SE kernel $\gamma_t \sim \mathcal{O}\left((\log t)^{d+1}\right)$
%    }
%   }
% } edge[pil] (fit1);
% }
%
% \uncover<1->{
% \node[st,right=9em of conv] (acc) {Solution accuracy};
% }
%
% \uncover<1->{
% \node[st,below=3em of acc] (loss) {$\max_{\*x\in D} \ell_h(\*x) \leq \epsilon$}
%   edge[pil] (acc)
%   edge[pil,<-] (eps);
% }
%
% \uncover<1->{
% \node[st,right=1.5em of loss] (rules) {Class. rules}
%   edge[pil] (loss);
% }
%
% \uncover<1->{ 
% \node[st,below=3em of loss] (est) {Correctly estimate $f$ w.h.p.}
%   edge[pil] (loss);
% }
%
% \uncover<1->{ 
% \node[st,right=1.5em of est] (delta) {$\delta$}
%   edge[pil] (est);
% }
%
% \uncover<1->{
% \node[st,below=3em of est] (large) {Conf. intervals are large enough}
%   edge[pil] (est)
%   edge[pil,<-] (t4);
% }
%\end{tikzpicture}
%\end{frame}

\begin{frame}
\begin{theorem}[Convergence of \acl]
For any $h\in\mathbb{R}$, $\delta \in (0, 1)$, and $\epsilon > 0$,
if $\beta_t = 2\log(|D|\pi^2 t^2/(6\delta))$, \acl terminates after
at most $T$ iterations, where $T$ is the smallest positive integer
satisfying
\begin{align*}
\frac{T}{\beta_T \gamma_T} \geq \frac{C_1}{4\epsilon^2},
%T/(\beta_T \gamma_T) \geq C_1/(4\epsilon^2),
\end{align*}
where $C_1 = 8 / \log(1 + \sigma^{-2})$.

@@

\begin{frame}
\begin{theorem}[Simplified]
If we choose $\beta_t$ large enough, then:
\begin{itemize}
\item<2-> \acl terminates after a number of iterations $T$
\begin{enumerate}
\item<3-> smoother kernel $\Rightarrow T \downarrow$
\item<4-> $\sigma \uparrow\ \Rightarrow T \uparrow$
\item<5-> ${\color<7>{red}\epsilon} \uparrow\ \Rightarrow T \downarrow$
\end{enumerate}
\item<6-> The solution returned is {\color<7>{red}$\epsilon$}-accurate with high probability
\end{itemize}
\end{theorem}
\end{frame}
